\section{Delete account}
In this section, a flow for deleting an account by the user is defined. 
\medskip

Delete account flow is given in Figure~\ref{fig:deleteAccount} and a successful flow is defined as follows:
    \begin{enumerate}
        \item Mobile MUST request a verification code from the Auth by submitting the email address of the user
              which is trying to delete the account and a token MUST be returned to the Mobile.
        \item Upon receiving a request to delete an account, the Auth MUST dispatch an email with the verification
              code to the Email.
        \item When the user enters verification code into the Mobile, the Mobile MUST authenticate the user locally 
              using a built-in biometry. Upon authenticating, the Mobile MUST send the token, user's email, and a 
              signature of the token, user's email, and verification code to the Auth to complete the process of 
              deleting the account.
    \end{enumerate}
    \input{diagrams/sequence/delete-account.tex}
If the account deletion is successful, the Mobile MUST delete any record of user's email, public key, and 
private key. The Auth SHOULD delete any record of user's email, public key, and private key.
\medskip

If the account deletion fails for any reason related to the protocol, an attempt to delete an account MUST be 
discarded. All of the following reasons are considered to be related to the protocol:
    \begin{itemize}
        \item An email is not associated with any account.
        \item Token does not exist.
        \item Token is not associated with a given email.
        \item Verification code entered into Mobile does not match the expected verification code.
        \item The signature cannot be verified by the associated public key.
        \item The signature is invalid.
    \end{itemize}
